\begin{thebibliography}{10}

%------ CAPÍTULO 1 - INTRODUÇÃO

\bibitem{eisberg}
	R.~Eisberg e R.~Resnick, \textsl{Física Quântica}, ed. Campus, 1979.

\bibitem{ashcroft}
	N.~W. Aschkroft e N.~D. Mermin, \textsl{Solid State Physics}, Saunders College Publishing, 1976.

\bibitem{kittel}
	C.~Kittel, \textsl{Introdução à Física do Estado Sólido}, John Wiley \& Sons, 1976.

\bibitem{bimberg}
	D.~Bimberg, M.~Grundmann  e N.~N. Ledentsov, \textsl{Quantum dot heterostructures}, John Wiley \& Sons, 1999.

\bibitem{dingle}
	R.~Dingle, W.~Wiegmann  e C.~H. Henry, \textsl{Quantum states of confined carriers in very thin \especie{Al_xGa_{1-x}As/GaAs/Al_xGa_{1-x}As} heterostructures}, Phys. Rev. Lett. \textbf{33}, 827 (1974).

\bibitem{celso}
	C.~de~Araújo~Duarte, \textsl{Processos de recombinação em pontos-quânticos em amostras com diferentes espessuras de camadas de \textrm{InAs} utilizando a técnica de fotoluminescência}, Dissertação de mestrado, \textsc{ifusp}, São Paulo (2002).	
	
\bibitem{mike}
	M.~J. da~Silva, \textsl{Crescimento e caracterização de pontos-quânticos de \textrm{InAs} auto-formados}, Dissertação de mestrado, \textsc{ifusp}, São Paulo (1999).

\bibitem{sandro}
	A.~L. Sperandio, \textsl{Crescimento epitaxial por feixe molecular de camadas para aplicação em dispositivos}, Dissertação de mestrado, \textsc{ifusp}, São Paulo (1998).

\bibitem{wood}
	D.~Wood, \textsl{Optoelectronic semiconductor devices}, Prentice Hall, 1994.

\bibitem{fafard1}
	S.~Fafard, K.~Hinzer, S.~Raymond, M.~Dion, J.~McCaffrey, Y.~Feng e S.~Charbonneau, \textsl{Red-emitting semiconductor quantum dot lasers}, Science \textbf{274}, 1350 (1996).

\bibitem{phillips}
	J.~Phillips, K.~Kamath  e P.~Bhattacharya, \textsl{Far-infrared photoconductivity in self-organized \textrm{InAs} quantum dots}, Appl. Phys. Lett. \textbf{72}, 2020 (1998).
	
\bibitem{joyce}
	P.~B. Joyce, T.~J. Krzyzewski, G.~R. Bell, T.~S. Jones, E.~C.~L. Ru e R.~Murray, \textsl{Optimizing the growth of \unit{1.3}{\micro\metre} \textrm{InAs/GaAs} quantum dots}, Phys. Rev. B \textbf{64}, 235317 (2001).

\bibitem{mike2}
	M.~J. da~Silva, S.~Martini, T.~E. Lamas, A.~A. Quivy, E.~C.~F. da~Silva e J.~R. Leite, \textsl{Low growth rate \textrm{InAs/GaAs} quantum dots for room-temperature luminescence over \unit{1.3}{\micro\metre}}, Microelec. J. \textbf{34}, 631 (2003).

\bibitem{mike3}
	M.~J. da~Silva, A.~A. Quivy, S.~Martini, T.~E. Lamas, E.~C.~F. da~Silva e J.~R. Leite, \textsl{\textrm{InAs/GaAs} quantum dots optically active at \unit{1.5}{\micro\metre}}, Appl. Phys. Lett. \textbf{82}, 2646 (2003).

\bibitem{kim}
	G.~H. Kim, J.~T. Nicholls, S.~I. Khondaker, I.~Farrer  e D.~A. Ritchie, \textsl{Tunning the insulator-quantum Hall liquid transitions in a two-dimensional electron gas using self-assembled \textrm{InAs}}, Phys. Rev. B \textbf{61}, 10910 (2000).
	
\bibitem{shields}
	A.~J. Shields, M.~P. O'Sullivan, I.~Farrer, D.~A. Ritchie, K.~Cooper, C.~L. Foden e M.~Pepper, \textsl{Optically induced bistability in the mobility of a two-dimensional electron gas coupled to a layer of quantum dots}, Appl. Phys. Lett. \textbf{74}, 735 (1999).

\bibitem{benoit}
	B.~Dubertret, P.~Skourides, D.~J. Norris, V.~Noireaux, A.~H. Brivanlou e A.~Libchaber, \textsl{In vivo imaging of quantum dots encapsulated in phospholipid micelles}, Science \textbf{298}, 1759 (2002).

\bibitem{coe}
	S.~Coe, W.~K. Woo, M.~Bawendi  e V.~Bulovi, \textsl{Electroluminescence from single monolayers of nanocrystals in molecular organic devices}, Nature \textbf{420}, 800 (2002).

\bibitem{venere}
	E.~Venere, \textsl{`Quantum dots' could form basis of new computers}, Purdue news, (Setembro de 2001).
		
\bibitem{baranov}
	A.~V. Baranov, V.~Davydov, H.-W. Ren, S.~Sugou  e Y.~Masumoto, \textsl{Phonon-enhanced intraband transitions in \textrm{InAs} self-assembled quantum dots}, J. of Luminescence \textbf{87-89}, 503 (2000).

\bibitem{mukai2}
	K.~Mukai, N.~Ohtsuka, H.~Shoji  e M.~Sugawara, \textsl{Phonon bottleneck in self-formed \textrm{InGaAs/GaAs} quantum dots by electroluminescence and time resolved photoluminescence}, Phys. Rev. B \textbf{54}, R5243 (1996).

%------ CAPÍTULO 2 - MBE E A FORMAÇÃO DOS PONTOS-QUÂNTICOS

\bibitem{ramachandran}
	T.~R. Ramachandran, R.~Heitz, P.~Chen  e A.~Madhukar, \textsl{Mass transfer in Stranski-Krastanow growth of \textrm{InAs} on \textrm{GaAs}}, Appl. Phys. Lett. \textbf{70}, 640 (1997).

\bibitem{heitz}
	R.~Reitz, T.~R. Ramachandran, A.~Kalburge, Q.~Xie, I.~Makhamezhanov, P.~Chen e A.~Madhukar, \textsl{Observation of reentrant 2D and 3D morphology transition in highly strained epitaxy: \textrm{InAs} on \textrm{GaAs}.}, Phys. Rev. Lett. \textbf{78}, 4071 (1997).

%------ CAPÍTULO 3 - AMOSTRAS

\bibitem{sakaki}
	H.~Sakaki, G.~Yusa, T.~Someya, T.~Noda, H.~Akiyama, Y.~Kadoya  e H.~Noge, \textsl{Transport properties of two-dimensional electron gas in \textrm{AlGaAs/GaAs} selectively doped heterojunctions with embedded \textrm{InAs} quantum dots}, Appl. Phys. Lett. \textbf{67}, 3444 (1995).

\bibitem{ribeiro}
	E.~Ribeiro, E.~Müller, T.~Heinzel, H.~Auderset, K.~Ensslin, G.~Medeiros-Ribeiro e P.~M. Petroff, \textsl{\textrm{InAs} self-assembled quantum dots as controllable scattering centers near a two-dimensional electron gas}, Phys. Rev. B \textbf{58}, 1506 (1998).

\bibitem{ryzhii}
	V.~Ryzhii, \textsl{The theory of quantum-dot infrared phototransistors}, Semicond. Sci. Technol. \textbf{11}, 759 (1996).

\bibitem{lee}
	S.-W. Lee, K.~Hirakawa  e Y.~Shimada, \textsl{Boud-to-continuum intersubband photoconductivity of self-assembled \textrm{InAs} quantum dots in modulation-doped heterostructures}, Appl. Phys. Lett. \textbf{75}, 1428 (1999).
	
%------ CAPÍTULO 4 - TÉCNICAS

\bibitem{look}
	D.~C. Look, \textsl{Electrical characterization of \textrm{GaAs} materials and devices}, John Wiley \& Sons, 1992.

\bibitem{schubert}	
	E. F. Schubert, \textsl{Delta-doping of semicondutors: Electronic, optical and structural properties of materials and devices} em \textsl{Epitaxial Microstructures}, vol.~40 de \textsl{Semiconductors and Semimetals}, Academic Press, 1994.

\bibitem{beck}
	W.~A. Beck e J.~R. Anderson, \textsl{Determination of electrical transport properties using a novel magnetic field-dependent Hall technique}, J. Appl. Phys. \textbf{62(2)}, 541 (1987).

\bibitem{bakarov}
	A.~K. Bakarov, A.~A. Bykov, N.~D. Aksenova, D.~V. Sheglov, A.~V. Latyshev e A.~I. Toropov, \textsl{Commensurate oscillations of the magnetoresistance of a two-dimensional electron gas in \textrm{GaAs} quantum wells with corrugated heteroboundaries}, JETP Letters \textbf{77}, 662 (2003).

\bibitem{bykov}
	A.~A. Bykov, A.~K. Bakarov, A.~V. Goran, N.~D. Aksenova, A.~V. Popova e A.~I. Toropov, \textsl{Semiclassical negative magnetoresistance of 2D electron gas caused by scattering by short-range and long-range potentials}, JETP Lett. \textbf{78}, 134 (2003).

\bibitem{mirlin}
	A.~D. Mirlin, D.~G. Polyakov, F.~Evers  e P.~Wölfle, \textsl{Quasiclassical negative magnetoresistance of a 2D electron gas:
  Interplay of strong scatterers and smooth disorder}, Phys. Rev. Lett. \textbf{87}, 126805--1 (2001).

\bibitem{ridley}
	B.~K. Ridley, \textsl{Quantum processes in semiconductors}, Oxford Science Publications, 1993.

\bibitem{isihara}
	A.~Isihara e L.~Smrc{\llap\textasciicaron}ka, \textsl{Density and magnetic field dependences of the conductivity of two-dimensional electron systems}, J. Phys. C: Solid State Phys. \textbf{19}, 6777 (1986).	

\bibitem{sarma}
	S.~D. Sarma e F.~Stern, \textsl{Single-particle time versus scattering time in an impure electron gas}, Phys. Rev. B \textbf{32}, 8442 (1985).

\bibitem{abrikosov}
	A.~A. Abrikosov, L.~P. Gorkov  e I.~E. Dzyaloshinski, \textsl{Methods of quantum field theory in statistical physics}, Prentice Hall, 1963.

\bibitem{ziman}
	J.~M. Ziman, \textsl{Principles of the theory of solids}, Cambridge University Press, 1972.

\bibitem{handbook}
	E.~Conwell, \textsl{Transport: the Boltzmann equation} em \textsl{Handbook on semiconductors}, vol.~1 de MOSS, North-Holland Publishing Company, 1982.

\bibitem{recipes}
	W.~H. Press, S.~A. Teukolsky, W.~T. Vetterling  e B.~P. Flanner, \textsl{Numerical recipes in Fortran}, Cambridge University Press, 1992.

\bibitem{smith}
	S.~W. Smith, \textsl{The scientist and engineers's guide to digital signal processing}, California Technical Publishing, 1999.

\bibitem{bockelmann}
	U.~Bockelmann e G.~Bastard, \textsl{Phonon scattering and relaxation in two-, one- and zero-dimensional electron gas}, Phys. Rev. B \textbf{42}, 8947 (1990).

\bibitem{fafard2}
	S.~Fafard, R.~Leon, D.~Leonard, J.~L. Merz  e P.~M. Petroff, \textsl{Phonons and radiative recombination in self-assembled quantum dots}, Phys. Rev. B \textbf{52}, 8 (1995).

\bibitem{inoshita}
	T.~Inoshita e H.~Sakaki, \textsl{Electron relaxation in quantum dot: significance of multiphonon processes}, Phys. Rev. B \textbf{46}, 7260 (1992).

\bibitem{mukai1}
	K.~Mukai, N.~Ohtsuka, H.~Shoji  e M.~Sugawara, \textsl{Emission from discrete levels in self-formed \textrm{InGaAs/GaAs} quantum dots by electric carrier injection: influence of phonon bottleneck}, Appl. Phys. Lett. \textbf{68}, 3013 (1996).

%------ CAPÍTULO 5 - INSTALAÇÕES

\bibitem{faissler}
	W.~L. Faissler, \textsl{An introduction to modern electronics}, John Wiley \& Sons, 1991.

\bibitem{oxford}
	\textsl{Practical cryogenics, an introduction to laboratory cryogenics}. Oxford Instruments Superconductivity Limited, 2000.
	
%------ CAPÍTULO 6 - RESULTADOS

\bibitem{kamiya}
	I. Kamiya, I. Tanaka e H. Sakaki, \textsl{Optical properties of near surface-InAs quantum dots and their formation processes}, Physica E \textbf{2}, 637 (1998).

\bibitem{fafard3}
	S. Fafard, S. Raymond, G. Wang, R. Leon, D. Leonard, S. Charbonneau, J. L. Merz, P. M. Petroff e J. E. Bowers, \textsl{Temperature effects on the radiative recombination in self-assembled quantum dots}, Surf. Sci. \textbf{361/362}, 778 (1996).

\bibitem{sanguinetti}
	S. Sanguinetti, M. Henini, M. G. Alessi, M. Capizzi, P. Frigeri e S. Franchi, \textsl{Carrier thermal escape and retrapping in self-assembled quantum dots}, Phys. Rev. B \textbf{60}, 8276 (1999).

\bibitem{Hlee}
	H. Lee, W. Yang e P.C. Sercel, \textsl{Temperature and excitation dependence of photoluminescence line shapein InAs/GaAs quantum-dot structures}, Phys. Rev B \textbf{55}, 9757 (1997).

\bibitem{xu}
	Z. Y. Xu, Z. D. Lu, Z. L. Yuan, X. P. Yang, B. Z. Zheng, J. Z. Xu, W. K. Ge, Y. Wang, J. Wang e L. L. Chang, \textsl{Thermal activation and thermal transfer of localized excitons in InAs self-organized quantum dots}, Superlattices and Microstructures \textbf{23}, 381 (1998).
	
\bibitem{celsoAD}
	C.~A. Duarte, E.~C.~F. da~Silva, A.~A. Quivy, M.~J. da~Silva, S.~Martini, J.~R. Leite, E.~A. Meneses  e E.~Lauretto, \textsl{Influence of the temperature on the carrier capture into self-assembled \textrm{InAs/GaAs} quantum dots}, J. Appl. Phys. \textbf{93}, 6279 (2003).
	
\bibitem{ademir}
	A.~Cavalheiro, \textsl{O efeito da fotocondutividade e a estrutura eletrônica de poços-quânticos de \textrm{GaAs/InGaAs/GaAs} com dopagem planar do tipo n na barreira}, Tese de doutorado, \textsc{ifusp}, São Paulo (2001).

\bibitem{ikai-lo}
	Ikai Lo and Y.~C.~Chang and H.~M.~Weng and J.-C.~Chiang, \textsl{Two-dimensional electron gas in $\delta$-doped quantum wells for photodetector application}, J. Appl. Phys. \textbf{81(12)}, 8112 (1997).

\bibitem{shaw}
	R.~W. Shaw e D.~E. Hill, \textsl{Shubnikov-de Haas oscillations in n-type \textrm{GaAs}}, Phys. Rev. B \textbf{1}, 658 (1970).

\bibitem{ademir1}
	A.~Cavalheiro, E.~C.~F. da~Silva, E.~K. Takahashi, A.~A. Quivy, J.~R. Leite e E.~A. Meneses, \textsl{Illumination as tool to investigate the quantum mobility of the two-dimensional electron gas in \textrm{Si} $\delta$-doped \textrm{GaAs}/ \especie{In_{0.15}Ga_{0.85}As}/\textrm{GaAs} quantum well}, Phys. Rev. B \textbf{65}, 111 (2002).

\bibitem{ademir2}
	A.~Cavalheiro, E.~C.~F. da~Silva, A.~A. Quivy, E.~K. Takahashi, S.~Martini, M.~J. da~Silva, E.~A. Meneses  e J.~R. Leite, \textsl{Influence of illumination on the quantum mobility of a two-dimensional electron gas in \textrm{Si} $\delta$-doped \textrm{GaAs}/\especie{In_{0.15}Ga_{0.85}As}/\textrm{GaAs} quantum wells}, J. Phys.: Condens. Matter \textbf{15}, 121 (2003).

\bibitem{henriques}
	A. B. Henriques, \textsl{Quantum and transport mobilities in $\delta$-doped semiconductors}, Phys. Rev. B \textbf{53}, 16365 (1996).

\bibitem{wojs1}
	L. Jacak, P. Hawrylack e A. Wójs, \textsl{Quantum dots}, ed. Springer, 1998.
	
\bibitem{wojs2}
	A. Wójs, P. Hawrylak, S. Fafard e L. Jacak, \textsl{Electronic structure and magneto-optics of self-assembled quantum dots}, Phys. Rev. B \textbf{54(8)}, 5604 (1996). 

\bibitem{yusa}
	G. Yusa e H. Sakaki, \textsl{Trapping of photogenerated carrieres by InAs quantum dots and persistent photoconductivity in novel GaAs/$n$-AlGaAs feld-effect transistor structures}, Appl. Phys. Lett. \textbf{70(3)}, 345 (1997).

\bibitem{zhukov}
	A. A. Zhukov, Ch. Weichsel, S. Beyer, S. Schnüll, Ch. Heyn e W. Hansen, \textsl{Transport properties of a two-dimensional electron gas in the vicinity of quantum dots in the limit of strong disorder}, Phys. Rev. B \textbf{67}, 125310 (2003).

\bibitem{jain}		
	S. C. Jain, M. Willander e H. Maes, \textsl{Stresses and strains in epilayers, stripes and quantum structures of III-V compound semiconductors}, Semicond. Sci. Technol. \textbf{11}, 641 (1996).

%-- APÊNDICE B - DEDUÇÃO DA EQUAÇÃO...

\bibitem{koenraad}
	P.~M. Koenraad, B.~F.~A. van Hest, F.~A.~P. Blom, R.~van Dalen, M.~Leys, J.~A. A.~J. Perenboom  e J.~H. Wolter, \textsl{Quantum- and transport electron mobility in the individual subbands of a two-dimensional electron gas in \textrm{Si}-$\delta$-doped \textrm{GaAs}}, Physica B \textbf{177}, 485 (1992).

\end{thebibliography}

%\bibitem{skuras}
%	E.~Skuras, R.~Kumar, R.~L. Williams, R.~A. Strading, J.~E. Dmochowski, E.~A. Johnson, A.~Mackinnon, J.~J. Harris, R.~B. Beall, C.~Skierbeszewski, J.~Singleton, P.~J. van~der Wel  e P.~Wisniewski, \textsl{Subband dependent mobilities and carrier saturation mechanisms in thin \textrm{Si} doping layers in \textrm{GaAs} in the high density limit}, Semicond. Sci. Technol., \textbf{6}, 535 (1991).

